\section{Security Aspects}
In this section the necessity of analysing web application is discussed.

The amount of vulnerabilities are growing every day as new software and features are released.
The attacker always has the advantage in terms of variety of attacks and because, how can one defend against something does not know.
So the element of surprise is certainly there.
As Bruce Schneier said:
\begin{quote}
`\textit{`Attackers are at an advantage in cyberspace – this will not always be true, but it’ll certainly be true for the next bunch of years – and that makes defense difficult.}''\cite{schneier_interview}  
\end{quote}

In regards to web application security there are popping up new technologies and old ones are evolving and developing new features.
These new technologies and features can be used by the attackers as well.
Therefore it is important to be updated on current and new technologies as a web security expert.\cite{web_security_importance}

The above shows the challenges that a security expert is facing every day.
So a piece of software that could help them find security vulnerabilities would result in them having more time to keep updated in their field.

The \citet{OWASP10} lists the most critical web application security flaws.
The web application security field agrees more or less on this list.
They recommend that each application is checked for these ten critical security flaws.

When examining the field for tools to help find security flaws in web applications the Python web applications were not covered satisfactory, see \cref{}\todo{ref til afsnit der sammenligner python tools}.
