\section{Security vulnerabilities}\label{security_vulnerabilities}
To make a tool that finds security vulnerabilities in a program is a very broad and ambitious task.
In order to make the task more manageable we have picked three common types of vulnerabilities from the OWASP list of top 10 vulnerabilities in web applications \cite{OWASP10}.
The chosen vulnerabilities will in the following be described and code examples will be presented showing the vulnerability in practice.
These code examples will later be used for testing the application.

\subsection{Injection attacks}\label{vulnerabilities:injection}
An injection is an uncontrolled use of user input that reaches an interpreter.
This could be a SQL interpreter, the command line or the Python interpreter.
If an injection vulnerability exists the user can send arbitrary commands to the server, and possibly access or alter data without authorisation.
The typical workaround is to sanitise the input so only the desired characters will be accepted. \citep{OWASPTOP10PDF}

The following will present two subgroups of injection attacks, SQL injections and command injections.

\subsubsection{SQL injection}
This description is based on \citet{sqlinjection}.
SQL injections happen when an application creates a query partly or entirely from user input without sanitising this input.
The user can escape the query and add an arbitrary query.
Depending on the system, the user can now change the database, read the database or in severe cases even execute system commands.

\paragraph{Example} An implementation of two possible SQL injections can be found in \cref{appendix:sqli}.
Here a database is setup with the library SQLAlchemy which has protection against SQL injection built in.
The problem is that it also supports raw SQL queries, and these examples utilise these.
The specific problems of the examples will be examined in the following.

\subparagraph{Naive SQL Handling}
The first example is a naive handling of SQL queries.
In this example the user has to input the whole query and the query is executed directly on the database.
The method for this is shown on \cref{sqli_naive}.

\begin{lstlisting}[style={python}, deletekeywords={file, FILE}, caption={An SQL statement is taken as input and executed directly on the database}, label={sqli_naive}, firstnumber=24]
@app.route('/raw')
def index():
    param = request.args.get('param', 'not set')
    result = db.engine.execute(param)
    print(User.query.all(), file=sys.stderr)
    return 'Result is displayed in console.'
\end{lstlisting}
This is a very unlikely case, but if it gets served by accident, it is a very dangerous vulnerability.

\subparagraph{SQL Filter}
The second example is where the user has to input the parameter for the filter method used for filtering the query.
The code for the method taking the parameter as input and querying the database with the filter parameter is shown on \cref{sqli_filter}.

\begin{lstlisting}[style={python}, caption={A filter string is taken as input and used as a parameter in the filter function.}, label={sqli_filter}, firstnumber=31]
@app.route('/filter')
def filter():
    param = request.args.get('param', 'not set')
    Session = sessionmaker(bind=db.engine)
    session = Session()
    result = session.query(User).filter("username={}".format(param))
    for value in result:
        print(value.username, value.email)
    return 'Result is displayed in console.'
\end{lstlisting}

Because the input string is not sanitised, the user can input whatever he wants, and an input like
\[2 ~ \text{or} ~ 1 = 1\]
will return all users in the database, which is of course not intended behaviour.
The key is to insert the \texttt{or} keyword which makes another statement possible.
The second statement just has to evaluate to true then all possible database entries are returned.
This ultimately means that the statement sent to the SQL interpreter looks for all users instead of just a particular one.

\subsubsection{Command Injection}
This description is based on \citet{commandinjection}.
Command injections are very similar to SQL injections, but instead of injecting commands into a database system, this attack makes it possible to inject commands into server shell.
The ability to perform commands on a server opens up possibilities to read password files, delete system files and various other dangerous operations.

\paragraph{Example}
An example of a command injection vulnerable application is presented in \cref{appendix:command_injection}.
In this example a textfile is being used as store for a site where customers can suggest items for a menu.
When customers enter an item into a textbox, it is stored on a new line in the file.
The content of the file is then read a displayed on the screen, showing all the suggesions.
The dangerous function is shown in \cref{command_injection_function} where it can be seen how the parameter from a textbox is being passed directly to the shell call in \cref{CI_call}.
Entering a string starting with a command separator (semicolon in bash and ampersand in windows cmd), makes it possible to interact directly with the system shell.
Thus entering a string like
\[ \text{; ls} \]
will print out the contents of folder containing the application.
Having access to the filesystem is obviously dangerous, as a malicious user can now perform arbitrary commands on the server.

\begin{lstlisting}[style=python, caption={The culprit making command injection possible. Param is not being escaped before being executed by the shell.}, label={command_injection_function}, firstnumber=13]
@app.route('/menu', methods=['POST'])
def menu():
    param = request.form['suggestion']
    command = 'echo ' + param + ' >> ' + 'menu.txt'

    subprocess.call(command, shell=True)

    with open('menu.txt','r') as f:
        menu = f.read()

    return render_template('command_injection.html', menu=menu)

\end{lstlisting}

\subsection{XSS}\label{vulnerabilities:xss}
Cross site scripting (abbreviated XSS) occur when a site takes untrusted data and sends it to other users without sanitisation.
The description i based on \citet{crosssitescripting}.
One example could be a comment section where an evil user sends in a comment containing some JavaScript.
When other users see this comment, their browser runs this JavaScript, which can access cookies or redirect to a malicious site.
Again, this can be prevented by sanitising user input that is stored.

\paragraph{Example}
A very simple example of a cross site scripting is presented in \cref{appendix:xss}.
The main part is displayed in \cref{xss}.
In \cref{xss:request} some input is taken and it is inserted into the result page in \cref{xss:replace}.
A link to the vulnerable web page can be constructed and sent to a unknowing user who opens the link and gets important information stolen.
In this example the input is not saved permanently, but if it was saved as for example a comment, a malicious user could inject arbitrary JavaScript, which all subsequent users would execute in their browsers.

\begin{lstlisting}[style=python, caption={The main part of the XSS example from \cref{appendix:xss}}, label={xss}, escapeinside={(*@}{@*)}, firstnumber=6]
@app.route('/XSS_param', methods =['GET'])
def XSS1():
    param = request.args.get('param', 'not set') (*@ \label{xss:request} @*)

    html = open('templates/XSS_param.html').read()
    resp = make_response(html.replace('{{ param }}', param))  (*@ \label{xss:replace}@*)
    return resp
\end{lstlisting}

\subsection{Path Traversal}\label{vulnerabilities:traversal}
Path traversal is when access to a resource gives unintended access to the file system of the server.
This description is based on \citet{pathtraversal}.
An example could be attaching an image to the page decided by some user input.
If the input is not validated an attacker will be able to traverse the file system with the parent directory element ('..'). 

\paragraph{Example}
An example of this vulnerability can be seen in \cref{appendix:path_traversal}.
The main part of the example is displayed in \cref{path_traversal}.
Providing the request parameter as \emph{?image\_name=../file.txt} will open and show file.txt in the browser.
This could possibly result in database content or passwords to be accessed by intruders.

\begin{lstlisting}[style=python, caption={The main part of the path traversal from \cref{appendix:path_traversal}}, label={path_traversal}, escapeinside={(*@}{@*)}, firstnumber=6]
@app.route('/')
def cat_picture():
    image_name = request.args.get('image_name')
    if not image_name:
        return 404
    return send_file(os.path.join(os.getcwd(), image_name)) (*@ \label{traversal:path} @*)

\end{lstlisting}

\section{Detecting vulnerabilities}\label{vulnerabilities:detecting}
Common for these three security vulnerabilities is that some user input reaches a sensitive piece of code.
An SQL injection happens when user input reaches a database query
Cross site scripting happens when user input reaches some HTML.
Path traversal happens when user input reaches a piece of code that performs file system access.

To detect these vulnerabilities we need to create a tool that can connect information about user input and sensitive code to detect when the operations performed are dangerous.
