\section{Python Web Frameworks}
This section contains two of the available Python web frameworks.
The web frameworks are chosen from \citet{python_web_frameworks_list}.
There are two sets of Python web frameworks, full-stack and non-full-stack frameworks, so one of each was chosen.
A full-stack framework is a framework that contains all you need to develop a web application.
A non-full-stack framework is a framework which not contains all packages to develop a complete web application.
This can be positive or negative but it means that the developer can chose his own package for the job.
First the Django web framework was chosen, which is a full-stack framework, because of it is probably the most popular one.
And the second choice one of the most popular non-full-stack framework is the Flask micro web framework.

\subsection{Django}
Django\cite{django_cite} is a web framework that contains all you need to make a complete web application.
Django is using the Model-View-Controller architecture pattern(MVC)\cite{leff2001web}.
It is build in a way that one has to add stuff in a specific way.
This means that there is not a lot customiseability in how the architecture of the project is built.

Django operates with a abstract concept of apps.
An app contains the following modules:
\begin{itemize}
\item Main module - where the app is starting to execute code.
\item Tests module - testing of the app.
\item Views module - visualisation of the app.
\item Urls module - maps urls to views.
\item Models module - models for instance from a database.
\item Apps module - nested apps.
\end{itemize}
A Django web application consists of a combination of apps.
The power of Django is the ease of reuse of an app as they are easily linked together using urls.

\subsection{Flask}
Flask\cite{flask_official} is a micro web framework.
Flask is highly customizable as you can chose your own architecture of your web application.
Also it is possible for instance to make your own form validation or use a form validation package that one wants.
Flask comes with the following features:
\begin{itemize}
\item Development server
\item Unit test support
\item REST support
\end{itemize}
The power of Flask is that the developer is able to customise everything.
